### 2024-05-17 neural-computer-latex/neural-computation.tex
topology hurts

% ----------------------------------------------------------------
% AMS-LaTeX Paper ************************************************
% **** -----------------------------------------------------------
\documentclass{amsart}
\usepackage{graphicx}
\usepackage{fix-cm}
\usepackage{amsmath, gauss}
\usepackage{etoolbox}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{circuitikz}
% This makes a command for Christoffel-Symbols
\usepackage{relsize}
\newcommand{\Christoffel}[2]{\ensuremath{{\mathlarger{\mathlarger\Gamma}}^{#1}\!\!\!_{#2}}}

\begin{document}

\title{Neural Computer\\{\bf Final Project}}%
\author{Renan Monteiro Barbosa}%
\date{05/16/2024}

\maketitle
\clearpage

% Reference to Shagrir Begin
% Shagrir 2022 p 240

Use Shagrir book The Nature of Physical Computing to formalize Computing as Modelling.

Sagrir proposes that computing is satisfied with modeling of the input-output type with some degree of morphism.

Assuming that computing is a process of the physical system that transforms (physical) input variables into output variables, the mirroring condition is as follows:

% Below is found at page 240

A physical system P is a computing system just in case:

\begin{enumerate}
    % ---------------------------------------------------------------------------------
    % 1-Input-Output Mirroring
    % ---------------------------------------------------------------------------------
    \item \textbf{Input-Output Mirroring}. The input-output function, g, of a given process in \textbf{P} preserves a certain relation, \underline{R}, in a target domain \textbf{T}: there is a mapping from \textbf{P} to \textbf{T} that maps g to \underline{R}, x to \underline{x}, y to \underline{y}, \dots , such that $g(x) = y$ iff $\left\langle \underline{x},\underline{y} \right\rangle\ \; \epsilon \; \underline{R}$. This means that g and \underline{R} share some formal relation \textbf{f}.
    % ---------------------------------------------------------------------------------
    % 2-Implementing
    % ---------------------------------------------------------------------------------
    \item \textbf{Implementing}. This process of \textbf{P}, whose input-output function is g, implements some formalism \textbf{S} whose input-output (abstract) function is \textbf{f}.
    % ---------------------------------------------------------------------------------
    % 3-Representing
    % ---------------------------------------------------------------------------------
    \item \textbf{Representing}. The input variables x of \textbf{P} represent the entities \underline{x} of \textbf{T}, and the output variables y of \textbf{P} represent the entities \underline{y} of \textbf{T}.
    % ----------------------------------------------------------------
\end{enumerate}

The underlined italicized symbols (such as x and y) to signify properties of the target domain.

% Reference to Shagrir End

% Reference to Neural Manifolds — Linear Algebra and Topology in Neuroscience Begin
% https://medium.com/bits-and-neurons/neural-manifolds-linear-algebra-and-topology-in-neuroscience-dde5a8181811

% https://www.nature.com/articles/nature13665

The paper Sadtler et. al. on Neural Manifolds cleverly establishes that neural activity is inherently constrained by properties of the physical network circuitry itself.

These constraints result in neural activity patterns that comprise a low-dimensional subspace — the manifold — within the larger possible high-dimensional neural space.

The authors relate this discovery to skill learning and adaptation

% Reference to Neural Manifolds — Linear Algebra and Topology in Neuroscience End

\clearpage

Important terms

metric tensor

Levi-Civita connection

Affine Connection

Covariant Derivative

Christoffel symbols $ \Christoffel{i}{jk} $

\end{document}
% ----------------------------------------------------------------

### 2024-05-21 neural-computer-ideas-latex/neural-computation.tex
trying things

--- 2024-05-17 neural-computer-latex/neural-computation.tex
@@
 
-\title{Neural Computer\\{\bf Final Project}}%
-\author{Renan Monteiro Barbosa}%
-\date{05/16/2024}
+% \title{Neural Computer\\{\bf Final Project}}%
+% \author{Renan Monteiro Barbosa}%
+% \date{05/16/2024}
 
-\maketitle
+% \maketitle
+% \clearpage
+
+\thispagestyle{plain}
+\begin{center}
+    \Large
+    \textbf{Neural Computer}
+
+    \vspace{0.4cm}
+    \large
+    Thesis Subtitle
+
+    \vspace{0.4cm}
+    \textbf{Renan Monteiro Barbosa}
+
+    \vspace{0.9cm}
+    \textbf{Abstract}
+
+    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. 
+    Turpis egestas pretium aenean pharetra magna ac placerat vestibulum. 
+    Morbi non arcu risus quis. Vel turpis nunc eget lorem dolor sed viverra. 
+    Arcu cursus euismod quis viverra nibh cras pulvinar mattis. 
+    Pretium fusce id velit ut tortor pretium viverra suspendisse potenti. 
+    Pellentesque diam volutpat commodo sed egestas egestas fringilla. 
+    Semper risus in hendrerit gravida. 
+    Est placerat in egestas erat imperdiet sed euismod nisi porta. 
+    Nunc vel risus commodo viverra maecenas accumsan lacus vel facilisis. 
+    Cras pulvinar mattis nunc sed blandit libero volutpat sed. 
+    Accumsan in nisl nisi scelerisque eu ultrices vitae auctor eu. 
+    At imperdiet dui accumsan sit amet nulla facilisi. 
+    Tempus quam pellentesque nec nam aliquam sem et tortor. 
+    Quam elementum pulvinar etiam non quam. 
+    Pretium aenean pharetra magna ac placerat vestibulum lectus mauris ultrices. 
+    Nunc aliquet bibendum enim facilisis. 
+    Lorem mollis aliquam ut porttitor leo a diam sollicitudin. 
+    Adipiscing elit pellentesque habitant morbi. 
+    Feugiat sed lectus vestibulum mattis ullamcorper velit sed ullamcorper morbi.
+\end{center}
+
 \clearpage
-
 % Reference to Shagrir Begin
@@
 
+References
+
+% Below References are found on the video
+% Your brain is moving along the surface of the torus - https://www.youtube.com/watch?v=9ujnZcaqf-4
+
+% Gardner, R. J. et al. Toroidal topology of population activity in grid cells. Nature 602, 123–128 (2022).
+% Pisokas, I., Heinze, S. & Webb, B. The head direction circuit of two insect species. eLife 9, e53985 (2020). https://elifesciences.org/articles/53985
+% Shilnikov, A. L. & Maurer, A. P. The Art of Grid Fields: Geometry of Neuronal Time. Front. Neural Circuits 10, (2016).
+% Moser, M.-B., Rowland, D. C. & Moser, E. I. Place Cells, Grid Cells, and Memory. Cold Spring Harb Perspect Biol 7, a021808 (2015).
+% Lewis, M., Purdy, S., Ahmad, S.
+& Hawkins, J.
+Locations in the Neocortex: A Theory of Sensorimotor Object Recognition Using Cortical Grid Cells.
+https://www.biorxiv.org/content/10.1101/436352v2 (2018) doi:10.1101/436352.
+
+% Mentioned by GUS on the TEMt
+% Connectome of the fly visual circuitry. - https://www.janelia.org/publication/connectome-fly-visual-circuitry
+
+% This is Referenced as the Function u(x)
+% Mathematical equivalence of two common forms of firing rate models of neural networks
+% https://pubmed.ncbi.nlm.nih.gov/22023194/
+
+\clearpage
+
 Important terms

### 2024-05-22 neural-computer-neurips/paper_neurips.tex
Added Neurips format

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
     \usepackage[nonatbib, final]{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{float}
\usepackage{graphicx}
\usepackage{subfig}

\usepackage{cite}

\title{TEM-t as The Universal Neural Computer}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{
  \textbf{Renan Monteiro Barbosa$^{1}$} \\ 
  $^{1}$University of West Florida \\ 
  \texttt{rmb54f@students.uwd.edu, \{email1, email2,\}@affiliation.edu}
}

\begin{document}

\maketitle

\begin{abstract}
The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on both the left- and right-hand margins. Use 10~point type, with a vertical spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered, bold, and in point size 12. Two line spaces precede the abstract. The abstract must be limited to one paragraph.

Tempus quam pellentesque nec nam aliquam sem et tortor. 
Quam elementum pulvinar etiam non quam. 
Pretium aenean pharetra magna ac placerat vestibulum lectus mauris ultrices. 
Nunc aliquet bibendum enim facilisis. 
Lorem mollis aliquam ut porttitor leo a diam sollicitudin. 
Adipiscing elit pellentesque habitant morbi. 
Feugiat sed lectus vestibulum mattis ullamcorper velit sed ullamcorper morbi.
\end{abstract}

\section{Introduction}

Advancements in the last few decades have brought us to a point at which what was thought to only be theorized by Tolman (1948) as he argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map. (note, try to make it sound like the theory of computing)

But what was missing from these early studies, was a way to address the neuronal mechanisms that led information to be stored as memory. Further development has shown that place cells are part of a wider network of spatially modulated neurons, including grid, border, and head direction cells, each with distinct roles in the representation of space and spatial memory.

Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014).

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}. The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}. The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}. The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}

% ###################################################################################################################
% ###################################################################################################################
% Adding a Single big Image
% ###################################################################################################################
% ###################################################################################################################
\section{Single image}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Fig.~\ref{image1} shows the NeurIPS logo.

\begin{figure}[H]
  \centering{\includegraphics[width=40mm]{images/logo-neurips.png}}
  \caption{Example of single image}
  \label{image1}
\end{figure}

% ###################################################################################################################
% ###################################################################################################################
% Adding multiple Images
% ###################################################################################################################
% ###################################################################################################################
\section{Multiple images}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Fig.~\ref{image1} shows the NeurIPS logo as well as Fig.~\ref{image2}.

\begin{figure}[H]
\centering
\subfloat[]{\includegraphics[width=40mm]{images/logo-neurips.png}} \quad \quad 
\subfloat[]{\includegraphics[width=40mm]{images/logo-neurips.png}} \quad
\caption{Examples for sub-images} \label{image2}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{40mm}
    \includegraphics[width=40mm]{images/logo-neurips.png}
    \caption{Logo image}
    \label{image3}
  \end{minipage} 
  \quad \quad \quad \quad \quad
  \begin{minipage}[b]{40mm}
    \includegraphics[width=40mm]{images/logo-neurips.png}
    \caption{Logo image}
    \label{image4}
  \end{minipage}
\end{figure}

% ###################################################################################################################
% ###################################################################################################################
% Example of Citations
% ###################################################################################################################
% ###################################################################################################################
\section{Citations}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. 
For example, \cite{reference_1} or \cite{reference_2} and \cite{reference_3} anre example for citations.

% ###################################################################################################################
% ###################################################################################################################
% Tables
% ###################################################################################################################
% ###################################################################################################################
\section{Tables}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. The Table~\ref{sample-table} shows an example of a table.

\begin{table}[H]
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Conclusions}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper. This example was prepared by Dennis Núñez Fernández.

\bibliography{references}{}
\bibliographystyle{plain}

\end{document}

### 2024-06-06 neural-computer-neurips/paper_neurips.tex
Adding several references
added intro

@@
 
+% #########################################################################################
+% #########################################################################################
+% Abstract
+% #########################################################################################
+% #########################################################################################
+
 \begin{abstract}
@@
 
+% #########################################################################################
+% #########################################################################################
+% Introduction
+% #########################################################################################
+% #########################################################################################
+
 \section{Introduction}
@@
 Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014).
+
+\cite{beiran2023parametric}
+
+(Must do a paper dump showcasing some advancements)
+In the last few decades we have seen many advancements in neuroscience.
+It is now possible to record activity from every neuron in a zebrafish larva’s brain while it is freely swimming and responding to stimuli (Kim et al.
+2017).
+We have a nearly complete map of one hemisphere of the fly brain, with every neuron and most of its synapses accounted for (Pipkin 2020).
+The neurons responsible for a mouse’s memory of an event can be recorded, tagged, and replayed by laser stimulation, causing the mouse to behave as if the event had happened again (CarrilloReid et al.
+2019; Ramirez et al.
+2013).
+(This references can be found on John M Beggs - The Cortex and the Critical Point)
+
+Such advancements brought to light evidence for what was once only a theory, for example, Tolman (1948) argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
+(note, try to make it sound like the theory of computing - references can be found on the TEM paper)
+
+But what was missing from these early studies, was a way to address the neuronal mechanisms that led information to be stored as memory.
+Further development has shown that place cells are part of a wider network of spatially modulated neurons, including grid, border, and head direction cells, each with distinct roles in the representation of space and spatial memory.
+
+The combination of all these technological and theoretical developments demonstrated through evidence and theoretical models that there is indeed a mechanistic basis for memory formation, this was shown in the Nobel winning work done by May-Britt Moser, Edvard I.
+Moser (reference the nobel prize)(Nobel prize winning Place Cells, Grid Cells, and Memory).
+This work has inspired new theories in theoretical-neuroscience that proposes the idea that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 - found in the TEM paper).
+(need to work on this paragraph)
+
+Limited evidence provided in recent work with grid cells has shown, there is mechanism generating invariant representations, by using simultaneous recordings from many hundreds of grid cells and subsequent topological data analysis that the joint activity of grid cells from an individual module (neuronal population) resides on a toroidal manifold as expected in a two-dimensional CAN (Continuous Attractor Network).
+The positions are maintained between environments and from wakefulness to sleep, demonstrating to be invariant representations.
+This research demonstrated ,with some limitations, network dynamics on a toroidal manifold and provided a population-level visualization of CAN dynamics in grid cells.
+(reference Toroidal topology of population activity in grid cells)
+
+Even though the limitations
+
+There is growing evidence to support that manifolds maintain a well-preserved covariance across tasks.
+These results support the view that complex computation emerges from the flexible activation of different combinations of “Neural modes” (Need to find a better term) which themselves arise from the Network Connectivity (reference to Hopfield is all you need and Transformers) (Cortical population activity within a preserved neural manifold underlies multiple motor behaviors, reference 8 for Emergence of universal computations through neural manifold dynamics)
+
+In this paper we want to show that there exists a morphism between Neuroscience models and existing NN models, so we can approximately represent the Neural Manifolds with the Transformers.
+
+Must note that we are not saying the brain is closely related to transformers, instead we are  using a mathematical relationship between the so popular transformers and the attractor neural networks that have been carefully formulated in neuroscience models as being an essential piece in forming invariant representations in a topological structure that facilitates the emergence of Computation Through Neural Population Dynamics.
+Additionally, by using a modified transformers model we can leverage several tools, techniques, software and hardware that have been matured and extensively tested given the popularity and widespread use of transformers.
+Further studies are required to develop and validate a better architecture that better represents Neural Population Dynamics.
 
@@
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Adding a Single big Image
-% ###################################################################################################################
-% ###################################################################################################################
+% #########################################################################################
+% #########################################################################################
+% Theory of Computing
+% #########################################################################################
+% #########################################################################################
+
+\section{Theory of Computing}
+
+Computing is not a new concept, there is historical evidence that the Greeks were already capable of performing computation to predict the astronomical movements giving a programmable input (Antikythera mechanism).
+
+% #########################################################################################
+% #########################################################################################
+% Example - Adding a Single big Image
+% #########################################################################################
+% #########################################################################################
+
 \section{Single image}
@@
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Adding multiple Images
-% ###################################################################################################################
-% ###################################################################################################################
+% #########################################################################################
+% #########################################################################################
+% Example - Adding multiple Images
+% #########################################################################################
+% #########################################################################################
+
 \section{Multiple images}
@@
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Example of Citations
-% ###################################################################################################################
-% ###################################################################################################################
-\section{Citations}
+% #########################################################################################
+% #########################################################################################
+% Example - Citations
+% #########################################################################################
+% #########################################################################################
+\section{Some other Section}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat.
-Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-For example, \cite{reference_1} or \cite{reference_2} and \cite{reference_3} anre example for citations.
+Citations examples used to be here
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Tables
-% ###################################################################################################################
-% ###################################################################################################################
+% #########################################################################################
+% #########################################################################################
+% Example - Tables
+% #########################################################################################
+% #########################################################################################
 \section{Tables}
@@
 
+% #########################################################################################
+% #########################################################################################
+% Conclusion
+% #########################################################################################
+% #########################################################################################
 \section{Conclusions}
@@
 
+% #########################################################################################
+% #########################################################################################
+% Acknowledgments
+% #########################################################################################
+% #########################################################################################
 \subsubsection*{Acknowledgments}
@@
 
+% #########################################################################################
+% #########################################################################################
+% References
+% #########################################################################################
+% #########################################################################################
+
 \bibliography{references}{}

### 2024-06-16 neural-computer-neurips/paper_neurips.tex
cool editing

--- 2024-05-22 neural-computer-neurips/paper_neurips.tex
@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-     \usepackage[nonatbib, final]{neurips_2019}
+% \usepackage[nonatbib, final]{neurips_2019}
+\usepackage[nonatbib, preprint]{neurips_2019}
 
@@
 
-\title{TEM-t as The Universal Neural Computer}
+\title{The Ghost in the Machine: Emergence of Computation in CW-complexes}
+% \title{TEM-t as The Universal Neural Computer}
 
@@
   $^{1}$University of West Florida \\ 
-  \texttt{rmb54f@students.uwd.edu, \{email1, email2,\}@affiliation.edu}
+  \texttt{rmb54f@students.uwf.edu}
 }
@@
 \maketitle
+
+% #########################################################################################
+% #########################################################################################
+% Abstract
+% #########################################################################################
+% #########################################################################################
 
@@
 
+% #########################################################################################
+% #########################################################################################
+% Introduction
+% #########################################################################################
+% #########################################################################################
+
 \section{Introduction}
 
-Advancements in the last few decades have brought us to a point at which what was thought to only be theorized by Tolman (1948) as he argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
+Advancements in the last few decades have brought us to a point at which what was thought to only be theorized by Tolman in 1948 \cite{tolman1948cognitive} as he argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
 (note, try to make it sound like the theory of computing)
@@
 
-Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014).
+Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 \cite{eichenbaum2014can}).
+
+\cite{beiran2023parametric}
+
+(Must do a paper dump showcasing some advancements)
+In the last few decades we have seen many advancements in neuroscience.
+It is now possible to record activity from every neuron in a zebrafish larva’s brain while it is freely swimming and responding to stimuli Kim et al.
+2017 \cite{kim2017pan}.
+We have a nearly complete map of one hemisphere of the fly brain, with every neuron and most of its synapses accounted for (Pipkin 2020 \cite{pipkin2020mapping}).
+The neurons responsible for a mouse’s memory of an event can be recorded, tagged, and replayed by laser stimulation, causing the mouse to behave as if the event had happened again (CarrilloReid et al.
+2019 \cite{carrillo2019controlling}; Ramirez et al.
+2013 \cite{ramirez2013creating}).
+
+Such advancements brought to light evidence for what was once only a theory, for example, Tolman in 1948 \cite{tolman1948cognitive} argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
+% (note, try to make it sound like the theory of computing - references can be found on the TEM paper)
+
+But what was missing from these early studies, was a way to address the neuronal mechanisms that led information to be stored as memory.
+Further development has shown that place cells are part of a wider network of spatially modulated neurons, including grid, border, and head direction cells, each with distinct roles in the representation of space and spatial memory.
+
+The combination of all these technological and theoretical developments demonstrated through evidence and theoretical models that there is indeed a mechanistic basis for memory formation, this was shown in the Nobel winning work done by May-Britt Moser, Edvard I.
+Moser \cite{moser2015place}.
+This work has inspired new theories in theoretical-neuroscience that , likewise to Tolman, proposes the idea that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 \cite{eichenbaum2014can}).
+% (need to work on this paragraph)
+
+% reference to Toroidal topology of population activity in grid cells
+Some evidence, eventhough limited, has shown in recent work with grid cells, \cite{gardner2022toroidal}, by using simultaneous recordings from many hundreds of grid cells and subsequent topological data analysis that the joint activity of grid cells from an individual module (neuronal population) resides on a toroidal manifold as expected in a two-dimensional CAN (Continuous Attractor Network), supporting the argument that there is indeed a mechanism generating invariant representations.
+The positions are maintained between environments and from wakefulness to sleep, demonstrating to be invariant representations.
+This research demonstrated, with some limitations, network dynamics on a toroidal manifold and provided a population-level visualization of CAN dynamics in grid cells.
+
+Even though the technological limitations to record population of neurons, these works provide growing evidence to hint that previous theories and intuitons formulated through theoretical neuro science were in the right path.
+
+There is growing evidence to support that manifolds maintain a well-preserved covariance across tasks.
+These results support the view that complex computation emerges from the flexible activation of different combinations of “Neural modes” (Need to find a better term) which themselves arise from the Network Connectivity (reference to Hopfield is all you need and Transformers) (Cortical population activity within a preserved neural manifold underlies multiple motor behaviors, reference 8 for Emergence of universal computations through neural manifold dynamics)
+
+In this paper we want to show that there exists a morphism between Neuroscience models and existing NN models, so we can approximately represent the Neural Manifolds with the Transformers.
+
+Must note that, likewise Whittington \cite{whittington2021relating} mentions, we are not saying the brain is closely related to transformers, instead we are using a mathematical relationship between the so popular transformers and the attractor neural networks that have been carefully formulated in neuroscience models as being an essential piece in forming invariant representations in a topological structure that facilitates the emergence of Computation Through Neural Population Dynamics.
+Additionally, we are exploiting this relationship by carefully crafting a modified transformers model so we can benefit from several engineering tools, techniques, softwares and hardware that have been matured and extensively tested given the popularity and widespread use of transformers.
+Further studies are required to develop and validate a better architecture that better represents Neural Population Dynamics.
+
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
 
@@
 
-\subsection{Retrieval of style files}
-
-The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}.
-The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.
-
-The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
 
@@
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Adding a Single big Image
-% ###################################################################################################################
-% ###################################################################################################################
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+\subsection{Retrieval of style files}
+
+The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}.
+The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.
+
+The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}
+
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Theory of Computing
+% #########################################################################################
+% #########################################################################################
+
+\section{Theory of Computing}
+
+Computing is not a new concept, there is historical evidence that the Greeks were already capable of performing computation to predict the astronomical movements giving a programmable input (Antikythera mechanism).
+
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Example - Adding a Single big Image
+% #########################################################################################
+% #########################################################################################
+
 \section{Single image}
@@
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Adding multiple Images
-% ###################################################################################################################
-% ###################################################################################################################
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Example - Adding multiple Images
+% #########################################################################################
+% #########################################################################################
+
 \section{Multiple images}
@@
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Example of Citations
-% ###################################################################################################################
-% ###################################################################################################################
-\section{Citations}
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat.
-Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-For example, \cite{reference_1} or \cite{reference_2} and \cite{reference_3} anre example for citations.
+% #########################################################################################
+% #########################################################################################
+% Example - Citations
+% #########################################################################################
+% #########################################################################################
+\section{Some other Section}
 
-% ###################################################################################################################
-% ###################################################################################################################
-% Tables
-% ###################################################################################################################
-% ###################################################################################################################
+Citations examples used to be here
+
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Example - Tables
+% #########################################################################################
+% #########################################################################################
 \section{Tables}
@@
 
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Conclusion
+% #########################################################################################
+% #########################################################################################
 \section{Conclusions}
@@
 
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Acknowledgments
+% #########################################################################################
+% #########################################################################################
 \subsubsection*{Acknowledgments}
@@
 
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% References
+% #########################################################################################
+% #########################################################################################
+
 \bibliography{references}{}

### 2024-06-22 neural-computer-neurips/paper_neurips.tex
added nice pics

@@
 
-\title{The Ghost in the Machine: Emergence of Computation in CW-complexes}
+\title{The Ghost in the Machine: Emergence of Computation through dynamics in CW-complexes}
 % \title{TEM-t as The Universal Neural Computer}
@@
 
-Advancements in the last few decades have brought us to a point at which what was thought to only be theorized by Tolman in 1948 \cite{tolman1948cognitive} as he argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
-(note, try to make it sound like the theory of computing)
+Idea of papers to cite, that demonstrate progress in how we record and map neurons.
 
-But what was missing from these early studies, was a way to address the neuronal mechanisms that led information to be stored as memory.
-Further development has shown that place cells are part of a wider network of spatially modulated neurons, including grid, border, and head direction cells, each with distinct roles in the representation of space and spatial memory.
-
-Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 \cite{eichenbaum2014can}).
-
-\cite{beiran2023parametric}
+Advances in two-photon calcium imaging in larval zebrafish (Ahrens et al.
+2012, Andalman et al.
+2019, Naumann et al.
+2016, Portugues et al.
+2014), Drosophila (Kim et al.
+2017 \cite{kim2017ring} ), rodents (Allen et al.
+2019, Chaudhuri et al.
+2019, Stringer et al.
+2019), and Caenorhabditis elegans (Kato et al.
+2015, Nichols et al.
+2017), as well as high channel count electrophysiology via NeuroPixels (e.g., Jun et al.
+2017, Stringer et al.
+2019, Trautmann et al.
+2019), have enabled measuring and manipulating neural activity at unprecedented scale.
+We believe these technologies will present new opportunities to test the CTD framework.
 
 (Must do a paper dump showcasing some advancements)
+
 In the last few decades we have seen many advancements in neuroscience.
@@
 Must note that, likewise Whittington \cite{whittington2021relating} mentions, we are not saying the brain is closely related to transformers, instead we are using a mathematical relationship between the so popular transformers and the attractor neural networks that have been carefully formulated in neuroscience models as being an essential piece in forming invariant representations in a topological structure that facilitates the emergence of Computation Through Neural Population Dynamics.
+
+(Cite the DeepSpeed-Megatron, Zero, SLURM, Scaling Laws and Nvidia research on training large models)
+
 Additionally, we are exploiting this relationship by carefully crafting a modified transformers model so we can benefit from several engineering tools, techniques, softwares and hardware that have been matured and extensively tested given the popularity and widespread use of transformers.
@@
 
+Start by defining Computing as Modelling, essential step to prove that the architecture is capable of Computing.
+
+It is crucial to distinguish between the notions of computational model and simulation on the one hand and computing-as-modeling on the other
+
+The computational model and simulation refer to the use of computers to model and simulate the behavior and processes of physical, biological, social, and other systems.
+They do not assume that modeling is an essential feature of computing; However, the claim is that computers can be, and are, used for modeling and simulating other phenomena.
+
+In contrast, the notion of computing-as-modeling is indifferent as to the actual use of computers for the purposes of modeling or simulating other phenomena; rather, the claim is that modeling is an essential element of the characterization of computing.
+
+The conclusion is that modeling is an essential element of physical computation, at least in current computational approaches in cognitive neuroscience.
+
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Why CW-complexes?
+% #########################################################################################
+% #########################################################################################
+
+\section{Why CW-complexes?}
+
+The far left panel is a simbplyfied cartoon depiction of a grid cell’s firing pattern in a two-dimensional environment.
+Making a cut through the center of four fields provides a diamond shape (second panel), which comprises the base unit.
+The dashed whiteline illustrates running the “longdistance” in the diamond between the furthest two fields.
+By connecting the bottom edge to the top edge, two “half-fields” are generated (third panel) which becomes a single field when connecting the opened ends (far right panel).
+Note that there are three lines on the completed torus.
+The dashed black lines represent the original cuts along made in the first panel.
+The white line resembles the trajectory necessary to connect the two furthest points in the diamond.
+Note that it makes one revolution per rotation.
+That is, the trajectory travels through the interior of the torus as well as along the exterior.
+
+\begin{figure}[H]
+    \centering{\includegraphics[width=150mm]{images/figure_grid-cell+to+torus.png}}
+    \caption{Schematic depiction of why grid cells map to a torus.}
+    \label{image1}
+\end{figure}
+
 % ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
@@
 
-\section{Single image}
+% \section{Single image}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
+% Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat.
@@
 
-\begin{figure}[H]
-  \centering{\includegraphics[width=40mm]{images/logo-neurips.png}}
-  \caption{Example of single image}
-  \label{image1}
-\end{figure}
+% \begin{figure}[H]
+%   \centering{\includegraphics[width=40mm]{images/logo-neurips.png}}
+%   \caption{Example of single image}
+%   \label{image1}
+% \end{figure}
 
@@
 
+\section{experimenting with Editing}
+
+Advancements in the last few decades have brought us to a point at which what was thought to only be theorized by Tolman in 1948 \cite{tolman1948cognitive} as he argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
+(note, try to make it sound like the theory of computing)
+
+But what was missing from these early studies, was a way to address the neuronal mechanisms that led information to be stored as memory.
+Further development has shown that place cells are part of a wider network of spatially modulated neurons, including grid, border, and head direction cells, each with distinct roles in the representation of space and spatial memory.
+
+Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 \cite{eichenbaum2014can}).
+
+\cite{beiran2023parametric}
+
 % ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀

### 2024-06-22 neural-computer-neurips/paper_neurips.tex
playing with formats

@@
 
-Additionally, we are exploiting this relationship by carefully crafting a modified transformers model so we can benefit from several engineering tools, techniques, softwares and hardware that have been matured and extensively tested given the popularity and widespread use of transformers.
+Additionally, we are exploiting this relationship by carefully crafting a modified transformers model so we can benefit from several technological advancements in how models are trained at scale ( \cite{DBLP:journals/corr/abs-1910-02054}, \cite{DBLP:journals/corr/abs-2201-11990}, \cite{DBLP:journals/corr/abs-2104-04473}, \cite{DBLP:journals/corr/abs-2001-08361} ), these advancements have been matured and extensively tested at production given the popularity and widespread use of transformers.
 Further studies are required to develop and validate a better architecture that better represents Neural Population Dynamics.
+
+% ZeRO: Memory Optimizations Towards Training Trillion Parameter Models \cite{DBLP:journals/corr/abs-1910-02054}
+
+% Using DeepSpeed and Megatron to Train Megatron-Turing NLG 530B \cite{DBLP:journals/corr/abs-2201-11990}
+
+% Efficient Large-Scale Language Model Training on GPU Clusters \cite{DBLP:journals/corr/abs-2104-04473}
+
+% Scaling Laws for Neural Language Models \cite{DBLP:journals/corr/abs-2001-08361}
 
@@
 
-\subsection{Retrieval of style files}
+% \subsection{Retrieval of style files}
 
-The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}.
+% The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}.
 The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.
 
-The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}
+% The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}
 
@@
 The conclusion is that modeling is an essential element of physical computation, at least in current computational approaches in cognitive neuroscience.
+
+At the book Shagrir - The Nature of Physical Computation \cite{shagrir2022nature}
+
+A physical system P is a computing system just in case:
+
+\begin{enumerate}
+    % ---------------------------------------------------------------------------------
+    % 1-Input-Output Mirroring
+    % ---------------------------------------------------------------------------------
+    \item \textbf{Input-Output Mirroring}.
+The input-output function, g, of a given process in \textbf{P} preserves a certain relation, \underline{R}, in a target domain \textbf{T}: there is a mapping from \textbf{P} to \textbf{T} that maps g to \underline{R}, x to \underline{x}, y to \underline{y}, \dots , such that $g(x) = y$ iff $\left\langle \underline{x},\underline{y} \right\rangle\ \; \epsilon \; \underline{R}$.
+This means that g and \underline{R} share some formal relation \textbf{f}.
+    % ---------------------------------------------------------------------------------
+    % 2-Implementing
+    % ---------------------------------------------------------------------------------
+    \item \textbf{Implementing}. This process of \textbf{P}, whose input-output function is g, implements some formalism \textbf{S} whose input-output (abstract) function is \textbf{f}.
+    % ---------------------------------------------------------------------------------
+    % 3-Representing
+    % ---------------------------------------------------------------------------------
+    \item \textbf{Representing}.
+The input variables x of \textbf{P} represent the entities \underline{x} of \textbf{T}, and the output variables y of \textbf{P} represent the entities \underline{y} of \textbf{T}.
+    % ----------------------------------------------------------------
+\end{enumerate}
+
+The underlined italicized symbols (such as x and y) to signify properties of the target domain.
 
@@
 % \end{figure}
+
+% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
+% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
+% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
+% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
+% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
+% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
+% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
+% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
+% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
+% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
+% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
+% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
+% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
+% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
+
+% #########################################################################################
+% #########################################################################################
+% Conclusion
+% #########################################################################################
+% #########################################################################################
+\section{Conclusions}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat.
+Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\section{experimenting with Editing}
+
+Advancements in the last few decades have brought us to a point at which what was thought to only be theorized by Tolman in 1948 \cite{tolman1948cognitive} as he argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
+(note, try to make it sound like the theory of computing)
+
+But what was missing from these early studies, was a way to address the neuronal mechanisms that led information to be stored as memory.
+Further development has shown that place cells are part of a wider network of spatially modulated neurons, including grid, border, and head direction cells, each with distinct roles in the representation of space and spatial memory.
+
+Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 \cite{eichenbaum2014can}).
+
+\cite{beiran2023parametric}
 
@@
 % #########################################################################################
-% Conclusion
-% #########################################################################################
-% #########################################################################################
-\section{Conclusions}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat.
-Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\section{experimenting with Editing}
-
-Advancements in the last few decades have brought us to a point at which what was thought to only be theorized by Tolman in 1948 \cite{tolman1948cognitive} as he argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map.
-(note, try to make it sound like the theory of computing)
-
-But what was missing from these early studies, was a way to address the neuronal mechanisms that led information to be stored as memory.
-Further development has shown that place cells are part of a wider network of spatially modulated neurons, including grid, border, and head direction cells, each with distinct roles in the representation of space and spatial memory.
-
-Bringing to surface a mechanistic basis for memory formation (Nobel prize winning Place Cells, Grid Cells, and Memory) which later has been suggested that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 \cite{eichenbaum2014can}).
-
-\cite{beiran2023parametric}
-
-% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
-% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
-% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
-% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
-% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
-% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
-% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
-% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
-% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
-% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
-% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
-% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
-% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
-% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
-% ⠀⠀⠈⠀⠀⠉⠀⠀⠀
-
-% #########################################################################################
-% #########################################################################################
 % Acknowledgments

### 2025-04-19 Neural-Manifolds/neural-manifolds_v0.tex
Studying Neuro Manifold Hypothesis

\documentclass{beamer}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{varwidth}
% \usepackage{caption}

\usepackage{subcaption}
\usepackage{media9}
\usepackage{multimedia}

\usepackage{amsfonts,amsmath,amssymb}
\usepackage{blkarray,booktabs,bigstrut}

\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{filecontents}
\usepackage{lmodern}

\usetikzlibrary{hobby}
\usetikzlibrary{decorations.shapes}
\usetikzlibrary{shadows.blur}

\definecolor{NvidiaGreen}{RGB}{118, 185, 0}

\usetheme{Madrid}
\setbeamertemplate{navigation symbols}{}

% Set the colors for various Beamer elements
\setbeamercolor{title}{fg=black, bg=NvidiaGreen} 
\setbeamercolor{frametitle}{fg=black, bg=NvidiaGreen} 
\setbeamercolor{item}{fg=black, bg=NvidiaGreen} 
\setbeamercolor{section in toc}{fg=black, bg=NvidiaGreen}
\setbeamercolor{author}{fg=white, 
        % bg=NvidiaGreen
    }
\setbeamercolor{date}{fg=white, 
        % bg=NvidiaGreen
    }

% Set the background to white for a clean presentation
\setbeamercolor{background canvas}{bg=white}

% #########################################################################################
% #########################################################################################
% Title
% #########################################################################################
% #########################################################################################

\begin{document}
{
\setbeamertemplate{background} 
{
    \includegraphics[width=\paperwidth,height=\paperheight]{images/Screenshot_9-12-2024_212019_.jpeg}
}
\title{\textbf{Computation and Neural Manifolds}}
\author[]{\textbf{Renan Monteiro Barbosa}}
% \date{\today}
\date[]{\textbf{2025}}
\maketitle
}

% #########################################################################################
% #########################################################################################
% Slide 1 - Intro
% #########################################################################################
% #########################################################################################

\section{Neural Manifolds}
\begin{frame}
\frametitle{\textbf{Neural Manifolds}}

Neural manifolds are being uncovered in many tasks aacrros the brain that help explain cognition

\begin{itemize}
    \item What are neural manifolds?
    \begin{enumerate}
        \item Neural manifolds are abstractions of neural trajectories, neurodynamical structure, often low-dimensional, in high-dimensional neural activity.
    \end{enumerate}
    \item What do neural manifolds do ?
    \begin{enumerate}
        \item Neural manifolds provide evidence for what is being computed by the brain.
        \item Neural manifolds provide evidence for how the brain computes.
    \end{enumerate}
\end{itemize}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 2 - Neural Activity
% #########################################################################################
% #########################################################################################

\section{Neural Activity}
\begin{frame}
\frametitle{\textbf{Neural Activity} }

Neural activity can be described as a high-dimensional neural spcace.

%  TODO - draw the Neural N-Space and the Manifold 3-Space

We start at some prat of the brain, the dimensionality is the number of neurons on that part, and each dimension is the firing rate of those neurons. The trajectory is the evolution of time

Manifolds are the abstraction fo the Neural N-Space to represent the activity over time

% In neural N-space, the activity of a neural network is described by a vector where each dimension represents the activity of a single neuron. This vector, or neural state, can be visualized as a point in an N-dimensional space, where N is the number of neurons. This framework allows for a more comprehensive understanding of network activity, including how it evolves and how different neurons interact.

% N-Dimensional State Space:
% Each neuron's activity (e.g., firing rate) contributes to a coordinate in this N-dimensional space. The instantaneous activity of all neurons collectively forms a point within this space, representing the current state of the network.

% Neural States and Manifolds:
% Neural activity is often not random; it tends to cluster around specific points or regions within the state space. These clusters or regions are known as intrinsic manifolds, representing the typical or relevant activity patterns of the network.

% Predicting and Interpreting Activity:
% By understanding the dynamics within this N-space, it becomes possible to predict future activity patterns or interpret the computational role of specific neural regions.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 3 - Intro
% #########################################################################################
% #########################################################################################

\section{Manifolds}
\begin{frame}
\frametitle{\textbf{Manifolds} }

Manifolds can be described as subspaces of vector spaces.

each vector is called the Basis vector

Basis Vectors: every point on manifold is a linear combination of these vectors.

%  TODO need work on this slide

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 4 - Neural Manifolds
% #########################################################################################
% #########################################################################################

\section{Neural Manifolds}
\begin{frame}
\frametitle{\textbf{Neural Manifolds} }
% repeat the intro slide
Neural manifolds are being uncovered in many tasks across the brain that help explain cognition.

\begin{itemize}
    \item What are neural manifolds?
    \begin{enumerate}
        \item Neural manifolds are abstractions of neural trajectories, neurodynamical structure, often low-dimensional, in high-dimensional neural activity.
    \end{enumerate}
    \item What do neural manifolds do ?
    \begin{enumerate}
        \item Neural manifolds provide evidence for what is being computed by the brain.
        \item Neural manifolds provide evidence for how the brain computes.
    \end{enumerate}
\end{itemize}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 5 - Temporal interval estimation
% #########################################################################################
% #########################################################################################

\section{Temporal interval estimation}
\begin{frame}
\frametitle{\textbf{Temporal interval estimation} }

In the temporal interval estimation task, monkeys estiamte the duration of a temporal interval.

% TODO - add picture form Sohn et al. 2019

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 6 - What counts as evidence for what is computed
% #########################################################################################
% #########################################################################################

\section{what is being computed?}
\begin{frame}
\frametitle{\textbf{what is being computed?} }
What counts as evidence for what is being computed ?

Generally, physical systems provide evidence for what is computed if:

\begin{enumerate}
    \item the proposed computation maps on to the behavior
    \item the behavior maps on to the properties of the part
    \item the part maps on to the proposed computation
\end{enumerate}

But first, what was the computation ?

% TODO - maybe here is a good point to reflect on Shagrir and theory of computation
% Can talk about mechanical computers

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 7 - Bayesian Computation
% #########################################################################################
% #########################################################################################

\section{Bayesian Computation}
\begin{frame}
\frametitle{\textbf{Bayesian Computation} }
A Bayesian computation was hypothesized for estimating intervals.

%  TODO add picture form Sohn et al. 2019

The temporal interval estimation task is being analyzed to discover how the brain is computing.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 8 - Behavior on Temporal Estimation Task
% #########################################################################################
% #########################################################################################

\section{Behavior on Temporal Estimation Task}
\begin{frame}
\frametitle{\textbf{Behavior on Temporal Estimation Task} }

Cool graphs go here
% TODO - Add the image from Sohn et al. 2019

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 9 - what is being computed?
% #########################################################################################
% #########################################################################################

\section{what is being computed?}
\begin{frame}
\frametitle{\textbf{what is being computed?} }
What counts as evidence for what is being computed ?

Generally, physical systems provide evidence for what is computed if:

\begin{enumerate}
    \item the proposed computation maps on to the behavior

    The Bayesian computation maps the bias in estimates of the interval

    \item the behavior maps on to the properties of the part

    How about the behaviour part mapping ?

    \item the part maps on to the proposed computation
\end{enumerate}

But first, what was the computation ?

% TODO - maybe here is a good point to reflect on Shagrir and theory of computation
% Can talk about mechanical computers

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 10 - Neural Manifolds on Temporal Estimation Task
% #########################################################################################
% #########################################################################################

\section{Neural Manifolds on Temporal Estimation Task}
\begin{frame}
\frametitle{\textbf{Neural Manifolds on Temporal Estimation Task} }

%  TODO - Add image from Sohn et al. 2019

Using Principal component Analysis, we can reduce and project this neural activity in a 3D space formed from the 3 principal components.

So know we can see the behavior maps on the properties of the part, for longer intervals there is a longer manifolds for shorter intervals there is shorter manifolds.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 11 - what is being computed?
% #########################################################################################
% #########################################################################################

\section{what is being computed?}
\begin{frame}
\frametitle{\textbf{what is being computed?} }
What counts as evidence for what is being computed ?

Generally, physical systems provide evidence for what is computed if:

\begin{enumerate}
    \item the proposed computation maps on to the behavior

    The Bayesian computation maps the bias in estimates of the interval

    \item the behavior maps on to the properties of the part

    the position along the curved manigolds maps the estimate of the interval

    \item the part maps on to the proposed computation

    Does the manifolds maps on to the computation?
\end{enumerate}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 12 - manifolds maps on to the computation?
% #########################################################################################
% #########################################################################################

\section{manifolds maps on to the computation?}
\begin{frame}
\frametitle{\textbf{manifolds maps on to the computation?} }
Different inputs determine the identity of the manifolds and the position in manifold space.

% TODO - add graph from the Sohn et al 2019

Different manifolds for different priors

Different states for different intervals within a distribution provide the input to the projection.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 13 - what is being computed?
% #########################################################################################
% #########################################################################################

\section{what is being computed?}
\begin{frame}
\frametitle{\textbf{what is being computed?} }
What counts as evidence for what is being computed ?

Generally, physical systems provide evidence for what is computed if:

\begin{enumerate}
    \item the proposed computation maps on to the behavior

    The Bayesian computation maps the bias in estimates of the interval

    \item the behavior maps on to the properties of the part

    the position along the curved manigolds maps the estimate of the interval

    \item the part maps on to the proposed computation

    the position along the curved manifold maps the Bayesian computation
\end{enumerate}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 14 - Evidence for what is being computed
% #########################################################################################
% #########################################################################################

\section{Evidence for what is being computed}
\begin{frame}
\frametitle{\textbf{Evidence for what is being computed} }
A three-way mapping between computation, part, and behavior is evidence for what is being computed.

The Bayesian computation maps the bias in estimates of the interval, the position along the curved manifolds maps the estimate of the interval, and the position along the curved manigolds maps the Bayesian computation.

Now we know how the Brain computes, can we use the Manifolds as evidence for What the Brain Computes ?

% What is Bayesian Computation
% Approximate Bayesian Computation: Introduction & Insurance Examples
% https://www.youtube.com/watch?v=pwVgIh1495A

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 15 - How it is being computed?
% #########################################################################################
% #########################################################################################

\section{How it is being computed?}
\begin{frame}
\frametitle{\textbf{How it is being computed?} }
Manifolds are also evidence for how something is being computed.

How the Bayesian estimates are being computed by neural activity.

The hypothesized computation was a projection from the manifold on to an encoding dimension.

% TODO add iamges from Sohn et al. 2019

the second computation was a porjection from the manifold onto what they called an encoding dimension.

This encoding Dimension was simply the vector described by the line that connected two points onto the manifold:

\begin{itemize}
    \item The point corresponding to the shortest interval to be estimated in a distribution
    \item The point corresponding to the longest interval in the distribution to be estimated
\end{itemize}

The geometry of projecting a curve onto a line is the compression of the lengths of the arcs along the curve that corresponds to segments of the line. This gives rise to the BIAS

Shorter interval corresponds to shorter length, Longer interval corresponds to longer length.

% TODO - describe a little about Discrete Differential Geometry and build it towrds the Information Geometry.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 16 - How it is being computed?
% #########################################################################################
% #########################################################################################

\section{How it is being computed?}
\begin{frame}
\frametitle{\textbf{How it is being computed?} }
Intermediate intervals are mapped onto intermediate points on the manifold.

% TODO add images from Sohn et al 2019

So the differences in the input to the vector projection give rise to differences in speed.

% This is depicted on the Projection onto u graph

x-axis is the projection onto the encoding dimension u and the y-axis is the speed through that manifold space along the curved 2D manifold and there is a law like correlation where the greate the projection onto U slower the speed .

We can observe a preservation in the projections of the relations between the speeds between the output of the computations and the properties of the manifolds and the proposed computation of vector projection

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 17 - How it is being computed?
% #########################################################################################
% #########################################################################################

\section{How it is being computed?}
\begin{frame}
\frametitle{\textbf{How it is being computed?} }
Manifolds provide evidence for how somehting is being computed.

Points on manifold map onto inputs and points on manifold or in manifold space map onto outputs of computation, and the relations between inputs and outputs of the computation have corresponding relations between points on manifold or in manifold space.

There is a Homomorphism, which is the preservation of relations between the outputs of the proposed computation and there is a corresponding relation in manifold space that preserves those relations.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 18 - Objections
% #########################################################################################
% #########################################################################################

\section{Objections}
\begin{frame}
\frametitle{\textbf{Objections} }
Arent all these computations the result of a single neuron activity ?

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 19 - Example of computation by neurons: perceptual decision making
% #########################################################################################
% #########################################################################################

\section{Example of computation by neurons: perceptual decision making}
\begin{frame}
\frametitle{\textbf{Example of computation by neurons: perceptual decision making} }
Example of computation by neurons: perceptual decision making

% TODO - add images on perceptual decision making

Stage 1: MT - Sensory Evidence

Stage 2: LIP - Accumulated Sensory Evidence

Stage 3: Choice - Categorization of evidence

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 20 - Objections Reply
% #########################################################################################
% #########################################################################################

\section{Objections Reply}
\begin{frame}
\frametitle{\textbf{Objections Reply} }
Arent all these computations the result of a single neuron activity ?

Reply:

Single Neurons cannot span a >1D space

But manifolds are often 1D

But often they are >1D

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 21 - Objections
% #########################################################################################
% #########################################################################################

\section{Objections}
\begin{frame}
\frametitle{\textbf{Objections} }

\begin{enumerate}
    \item Arent all these computations the result of a single neuron activity ?
    \item Arent all these computations the result of population activity ?
\end{enumerate}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 22 - Objections Reply
% #########################################################################################
% #########################################################################################

\section{Objections Reply}
\begin{frame}
\frametitle{\textbf{Objections Reply} }

\begin{enumerate}
    \item Arent all these computations the result of a single neuron activity ?
    \item Arent all these computations the result of population activity ?
\end{enumerate}

Reply

\begin{itemize}
    \item Different population patterns can result in the same manifold.
    \item Population equivalence classes are not the right type of thing to transform inputs into outputs or to structure dynamics.
    \item What all the elements of the population equivalence class have in common are the dynamics -> collapses into manifold view
\end{itemize}

In other words, different patterns of spiking activity across the population results in the same low dimensional dynamical structure.

In other works, the neural trajectories whose abstractions are the neural manifolds.

This implies that there are not dedicated neurons that encode the manifold dimensions because there is a variety of diversity of population activity patterns that can give rise to it.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 23 - Objections
% #########################################################################################
% #########################################################################################

\section{Objections}
\begin{frame}
\frametitle{\textbf{Objections} }

\begin{enumerate}
    \item Arent all these computations the result of a single neuron activity ?
    \item Arent all these computations the result of population activity ?
    \item Arent all these computations the result of other features of the population ?
\end{enumerate}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 24 - Objections Reply
% #########################################################################################
% #########################################################################################

\section{Objections Reply}
\begin{frame}
\frametitle{\textbf{Objections Reply} }

\begin{enumerate}
    \item Arent all these computations the result of a single neuron activity ?
    \item Arent all these computations the result of population activity ?
    \item Arent all these computations the result of other features of the population ?
\end{enumerate}

Reply

\begin{itemize}
    \item The weight matrix is not sufficient: difference numbers of neurons and different sets of weights are sufficient for the same manifold.
    \item What difference weight matrices have in common are just those dynamics -> collapses into manifold view.
    \item Similar point applies for other features of population (e.g., noise correlations)
\end{itemize}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 25 - Neurocomputational Manifold Hypothesis
% #########################################################################################
% #########################################################################################

\section{Neuraocomputational Manifold Hypothesis}
\begin{frame}
\frametitle{\textbf{Neuraocomputational Manifold Hypothesis} }

NCM - Neural Trajectory n on a manifold m in manifold space S is a computation of a function f over inputs i and outputs o only if there is:

\begin{itemize}
    \item input mapping: neural trajectory n starts on m that maps onto i;
    \item output mapping: neural trajectory n ends at a point in S that maps onto o; and
    \item relation mapping: for every relation R between pairs of i and o of f, there is a relation R' between pairs of points from n on m and in S.
\end{itemize}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 26 - Objections
% #########################################################################################
% #########################################################################################

\section{Objections}
\begin{frame}
\frametitle{\textbf{Objections} }

\begin{enumerate}
    \item Arent all these computations the result of a single neuron activity ?
    \item Arent all these computations the result of population activity ?
    \item Arent all these computations the result of other features of the population ?
    \item Manifolds arent real.
\end{enumerate}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 27 - Inpute-State-Output Analysis of Computation
% #########################################################################################
% #########################################################################################

\section{Inpute-State-Output Analysis of Computation}
\begin{frame}
\frametitle{\textbf{Inpute-State-Output Analysis of Computation} }

A physical system P implements a CSA M if there is a vectorization of internal states of P into components $\left[s^1, s^2, \cdots\right]$, and a mapping f from the substates $s^j$ into corresponding substates $S^j$ of M, along with similar vectorizations and mapping for inputs and outputs, such that for every state-transition rule $\left(\left[I^1, \cdots, I^k\right],\left[S^1, S^2, \cdots\right]\right) -> \left(\left[S^{\prime 1}, S^{\prime 2}, \cdots\right],\left[O^1, \cdots, O^i\right]\right)$ of M: if P is in internal state $\left[s^1, s^2, \cdots\right]$ and receiving input $\left[i^i, \cdots, i^n\right]$ which map to formal state and input $\left[S^1, S^2, \cdots\right]$ and $\left[I^1, \cdots, I^k\right]$ respectively, this reliably causes it to enter an internal state and produce an output that map to $\left[S^{\prime 1}, S^{\prime 2}, \cdots\right]$ and $\left[O^1, \cdots, O^i\right]$ respectively.

Chalmers 2011, p.329

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 28 - Inpute-State-Output Analysis of Computation Reply
% #########################################################################################
% #########################################################################################

\section{Inpute-State-Output Analysis of Computation Reply}
\begin{frame}
\frametitle{\textbf{Inpute-State-Output Analysis of Computation Reply} }

This is different than the computations outlined in the temporal interval estimation that rely on manifolds.

The computation or those trajectories does not rely on these sort of state to state transformations.

Because across different manifolds such as the transformation from the estimation epic one-dimensional manifolds to the production epic two-dimensional may involve state-to-state changes, but it also may involve changes in manifold space altogether.

Also part of the Manifold hypothesis is the preservation of the relations, the homomorphism and that requirement is absent from the Inpute-State-Output Analysis of Computation. Thus this analysis is insufficient.

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 29 - Input-Output Analysis of Computation
% #########################################################################################
% #########################################################################################

\section{Input-Output Analysis of Computation}
\begin{frame}
\frametitle{\textbf{Input-Output Analysis of Computation} }

Cummins says that "to compute a function g is to execute a program that gives o as its output on input i just in case $g(i) = o$. Computing reduces to program execution, so our problem reduces to explaining what it is to execute a program ... program exectuion involves steps, and to treat each elementary step as a function that the executing system simply satisfies. To execute a program is to satisfy steps" - Cummins 1989, p. 91-92

Temporal Interval estimation cannot be described as program execution

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 30 - Modeling Analysis of Computation
% #########################################################################################
% #########################################################################################

\section{Modeling Analysis of Computation}
\begin{frame}
\frametitle{\textbf{Modeling Analysis of Computation} }

A physical system P is a computing system just in case:

\begin{enumerate}
    % ---------------------------------------------------------------------------------
    % 1-Input-Output Mirroring
    % ---------------------------------------------------------------------------------
    \item \textbf{Input-Output Mirroring}. The input-output function, g, of a given process in \textbf{P} preserves a certain relation, \underline{R}, in a target domain \textbf{T}: there is a mapping from \textbf{P} to \textbf{T} that maps g to \underline{R}, x to \underline{x}, y to \underline{y}, \dots , such that $g(x) = y$ iff $\left\langle \underline{x},\underline{y} \right\rangle\ \; \epsilon \; \underline{R}$. This means that g and \underline{R} share some formal relation \textbf{f}.
    % ---------------------------------------------------------------------------------
    % 2-Implementing
    % ---------------------------------------------------------------------------------
    \item \textbf{Implementing}. This process of \textbf{P}, whose input-output function is g, implements some formalism \textbf{S} whose input-output (abstract) function is \textbf{f}.
    % ---------------------------------------------------------------------------------
    % 3-Representing
    % ---------------------------------------------------------------------------------
    \item \textbf{Representing}. The input variables x of \textbf{P} represent the entities \underline{x} of \textbf{T}, and the output variables y of \textbf{P} represent the entities \underline{y} of \textbf{T}.
    % ----------------------------------------------------------------
\end{enumerate}

Shagrir 2022, p.240

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide 30 - Modeling Analysis of Computation
% #########################################################################################
% #########################################################################################

\section{Modeling Analysis of Computation Reply}
\begin{frame}
\frametitle{\textbf{Modeling Analysis of Computation Reply} }

The same function describes a relation between states of the physical system and states of the computation, but this seems false because some functional relations between physical system States simply do not stand in a counterpart relation in the sates of the computation for example different lenghts of temporal intervals stand in longer than and shorter than temporal relations, but the manifold states which have the best claim to satisfy the modeling account do not stand in temporal relations rather they stand in manifold spatial relations.

Shagrir uses a lot the occular motion integrator as example. The occular motor integrator maps certain neural inputs to neural outputs and this mapping input output process mirrors the relation between movements and positions of the eye.

% TODO - Need to work on this

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide XX - Conclusion
% #########################################################################################
% #########################################################################################

\section{Conclusion}
\begin{frame}
\frametitle{Conclusion}

Manifolds provide evidence for what is being computed and how it is being computed in the brain

\begin{itemize}
    \item Manifolds are abstractions from sets of neural trajectory and are structure in neural dynamics
    \item Manifolds are evidence for what and how the brain computes
    \item Manifolds can constrain accounts of neural computation.
\end{itemize}

\end{frame}

% #########################################################################################
% #########################################################################################
% Slide XX - References
% #########################################################################################
% #########################################################################################

\section{References}
\begin{frame}
\frametitle{References}

The Slides 1 through 30 are based on the presentation:

Computation and Neural Manifolds

https://www.youtube.com/watch?v=zgP8SipIuHA

Galego et al. 2017

Neural Manifolds for the Control of Movement

https://pubmed.ncbi.nlm.nih.gov/28595054/

Sohn et al 2019

Bayesian Computation through Cortical Latent Dynamics

https://www.sciencedirect.com/science/article/pii/S0896627319305628

\end{frame}

% #########################################################################################
% #########################################################################################
% #########################################################################################
% #########################################################################################

% ⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣀⣀⣀⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀
% ⠀⠀⠀⠀⠀⠀⢀⣠⠤⠖⠈⠉⠉⠀⠀⠀⠀⠉⠢⡀⠀⠀⠀⠀⠀⠀
% ⠀⠀⠀⠀⠀⣴⠏⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⢦⡀⠀⠀⠀⠀
% ⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⠞⠋⢙⣦⡈⣷⡄⠀⠀⠀
% ⠀⣀⠶⠁⠀⠀⣀⣀⡀⠀⠀⠀⠀⠀⡴⠁⠀⠀⠿⢿⡟⣌⢿⠀⠀⠀
% ⣠⡿⠀⢠⣜⠉⠀⠀⠙⢷⢄⠀⠀⠀⢧⠀⠀⠀⠀⠀⠀⠘⡆⢧⡀⠀
% ⣯⠃⠀⢾⣿⠗⠀⠀⠀⠀⡽⠀⠀⠀⠈⠳⢄⣀⠀⠀⠀⡰⠃⠘⣵⡄
% ⡏⠀⠀⠘⡄⠀⠀⠀⣠⠞⠁⠀⠀⠀⠀⠀⠀⠀⠉⠉⠁⠀⠀⠀⢱⡇
% ⡅⠀⠀⠀⠙⠒⠔⠚⠁⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⡇
% ⣧⡀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⠀⠀⠀⠀⠀⠀⠀⡗
% ⡿⡇⠀⠀⠀⠀⠀⠀⠀⠀⠀⢠⡀⠀⠀⠀⠀⢸⡇⠀⠀⠀⠀⠀⠀⣇
% ⠹⣷⠀⠀⠀⠀⠀⠀⠀⠀⠀⠈⠷⣤⣤⣤⣤⠞⠁⠀⠀⠀⠀⠀⠀⣸
% ⠀⠸⣇⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⣰⠇
% ⠀⠀⢇⠳⣄⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⢀⡏⠀
% ⠀⠀⠈⠀⠀⠉⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀⠀

% #########################################################################################
% #########################################################################################
% #########################################################################################
% #########################################################################################

\end{document}

### 2025-04-19 Neural-Manifolds/neural-manifolds_v0.tex
adding cool images

@@
 
+\centering
+\begin{minipage}{1\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/gallego_et_al-2017_01.PNG} % Replace with your image file
+    \captionof{figure}{manifold}
+\end{minipage}
+
+Trajectory of time-varying population activity in the neural space of the three recorded neurons (black).
+The trajectory is mostly confined to the neural manifold, a plane shown in gray and spanned by the neural modes $u_1$ and $u_2$.
+
 \end{frame}
@@
 % TODO - add picture form Sohn et al. 2019
+
+\centering
+\begin{minipage}{1\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_01.PNG} % Replace with your image file
+    \captionof{figure}{temporal interval estimation}
+\end{minipage}
+
+Schematic of a single trial of the ReadySet-Go task.
+The animal has to estimate a sample interval, ts, between Ready and Set (estimation epoch), and produce a matching interval, tp, after Set with a delayed response (Go) via a saccade or a movement of the joystick (production epoch).
 
@@
 
+\centering
+\begin{minipage}{1\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_02.PNG} % Replace with your image file
+    \captionof{figure}{temporal interval estimation}
+\end{minipage}
+
 \end{frame}
@@
 % TODO - Add the image from Sohn et al. 2019
+
+\centering
+\begin{minipage}{1\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_03.PNG} % Replace with your image file
+    \captionof{figure}{temporal interval estimation}
+\end{minipage}
+
+% Behavior.
+Top: a representative session for monkey H showing tp pooled across effectors and target directions (small dots, individual trials; large open circles, average tp per ts; solid lines, Bayesian model; diagonal, unity line).
+The horizontal location of dots was jittered to facilitate visualization.
+Right: histograms of tp for the overlapping ts (horizontal dashed line) for the two prior conditions (orange, Short; blue, Long; triangles, averages).
+Top-left inset: average error (i.e., bias) for each ts (circles, data; solid lines, Bayesian model).
+Bottom-right inset: histogram of regression slopes relating tp to ts across sessions (red, Short; blue, Long; triangles, averages).
+Bottom: the same as top for monkey G.
 
@@
 So know we can see the behavior maps on the properties of the part, for longer intervals there is a longer manifolds for shorter intervals there is shorter manifolds.
+
+\centering
+\begin{minipage}{1\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_04.PNG} % Replace with your image file
+    \captionof{figure}{temporal interval estimation}
+\end{minipage}
 

### 2025-04-24 Neural-Manifolds/neural-manifolds_v0.tex
one potato at the time
crazy ideas

@@
 % TODO - add graph from the Sohn et al 2019
+% Need to add the arrows to the Graph
 
@@
 Different states for different intervals within a distribution provide the input to the projection.
+
+\centering
+\begin{minipage}{1\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_04.PNG} % Replace with your image file
+    \captionof{figure}{temporal interval estimation}
+\end{minipage}
 
@@
 \frametitle{\textbf{How it is being computed?} }
+
+% Might need to break the information on more slides
+
 Manifolds are also evidence for how something is being computed.
@@
 
-the second computation was a porjection from the manifold onto what they called an encoding dimension.
+\centering
+\begin{minipage}{1\textwidth}
+    \centering
+    \includegraphics[width=0.2\textwidth]{images/Sohn_et_al-2019_05.PNG} % Replace with your image file
+    \captionof{figure}{temporal interval estimation}
+\end{minipage}
+
+the second computation was a projection from the manifold onto what they called an encoding dimension.
 
@@
 % #########################################################################################
+% Slide XX - Crazy Ideas
+% #########################################################################################
+% #########################################################################################
+
+\section{Crazy Ideas}
+\begin{frame}
+\frametitle{Crazy Ideas}
+
+Take the idea of the Feynman's path integral as inspiration.
+
+The brain computes by creating and manipulating representations of reality, effectively building models that allow for prediction and manipulation of the world.
+Computing is not just about processing data (the change of states), but about creating and using representations that have meaning.
+
+These representations can be expressed as manifolds.
+
+As it tranverses the manifold we observe a change of phase which can be descirbed in information geometry and the former statistical mechanics as related to likelihood.
+(attention to the Hodge operator).
+If we consider that there are many paths to start at a simplicial representation and to achive a simplicial go and the path is the computation.
+We can say that all computations that are within the path of least ACTION constructively interferes and all other paths destructively interferes.
+
+Need to extend the Approximate Bayesian Computation (ABC)
+
+% the Hodge star operator can be used to define duality in the space of probability distributions. 
+% The Hodge operator can be used to relate likelihood functions (which express the probability of observing data given a model) to the geometry of the model space.
+% ℏ (pronounced "h-bar") represents the reduced Planck constant
+
+\end{frame}
+
+% #########################################################################################
+% #########################################################################################
 % #########################################################################################

### 2025-04-25 Neural-Manifolds/neural-manifolds_v0.tex
added lagrangian more or less

@@
 % #########################################################################################
+% Slide XX - Path Integral
+% #########################################################################################
+% #########################################################################################
+
+\section{Path Integral}
+\begin{frame}
+\frametitle{Path Integral}
+
+Take the idea of the Feynman's path integral as inspiration.
+
+$A = e^{i \phi}$
+
+$\Delta \phi = \frac{2 \pi}{\lambda}\Delta x - 2\pi f \Delta t$
+
+$A = e^{i \sum \Delta \phi} = e^{i \sum \frac{2 \pi}{\lambda}\Delta x -2 \pi f \Delta t}$
+
+de Broile: $\lambda = \frac{h}{mv}$, Einstein-Planck: $E = hf -> f = \frac{E}{h}$, Simplified Planck Constant $\hbar = \frac{h}{2\pi}$
+
+$A = e^{i \sum \frac{2\pi mv}{h} \Delta x -2\pi \frac{E}{h} \Delta t}$
+
+$A = e^{i \frac{\sum mv \Delta x - E \Delta t}{\hbar}}$
+
+$A = e^{i \frac{\sum \left( mv \frac{\Delta x}{\Delta t} - E\right) \Delta t}{\hbar}}$
+
+For a very small $\Delta t$:
+
+$A = e^{i \frac{\int \left( mv \frac{d x}{d t} - E\right) d t}{\hbar}}$
+
+$mv \frac{d x}{d t} = mv^{2}$ and $E = T + V = \frac{1}{2} mv^{2} + V$
+
+\end{frame}
+
+% #########################################################################################
+% #########################################################################################
+% Slide XX - Path Integral
+% #########################################################################################
+% #########################################################################################
+
+\section{Path Integral}
+\begin{frame}
+\frametitle{Path Integral}
+
+$A = e^{i \frac{\int \left( mv^{2} -\frac{1}{2} mv^{2} - V\right) d t}{\hbar}}$
+
+$A = e^{i \frac{\int \left( \frac{1}{2} mv^{2} - V\right) d t}{\hbar}}$
+
+Classical Action: $S = \int \left( \frac{1}{2} mv^{2} - V\right) d t$ therefore $A = e^{i \frac{S}{\hbar}}$
+
+$A = e^{i \frac{S}{\hbar}}$ given $\hbar \approx 10^{-34} J \cdot s$
+
+$dS = S[q] - S[p] = 0$
+
+So the path chosen is the path of least action which is the path where all phases interfere cosntructively.
+
+If you observe closely this resembles the Lagrangian.
+
+$S = \int_{t_{1}}^{t_{2}} \left(T - V\right)dt = \int_{t_{1}}^{t_{2}} Ldt$
+
+T being kinect energy and V being potential energy.
+
+\end{frame}
+
+% #########################################################################################
+% #########################################################################################
+% Slide XX - Path Integral
+% #########################################################################################
+% #########################################################################################
+
+\section{Path Integral}
+\begin{frame}
+\frametitle{Path Integral}
+
+Lagrangian Examples
+
+Classical mechanics: $L_{CM} = T - V$
+
+Special relativity $L_{SR} = -mc^{2} \sqrt{1 - \frac{v^{2}}{c^{2}}}$
+
+% https://physics.stackexchange.com/questions/755822/what-is-the-full-qed-lagrangian-with-physics-units-written-out
+
+% https://mathworld.wolfram.com/MinkowskiMetric.html
+
+Electrodynamics $L_{EM} = -1\frac{1}{4} F^{\mu \nu}F_{\mu \nu} + \frac{1}{c} j_{\mu}A_{\mu}$
+
+% TODO - need to properly write the General Relativity and QED
+
+General Relativity $L_{GR} = -mc^{2} \sqrt{-c^{2}g_{\mu \nu}}$
+
+\end{frame}
+
+% #########################################################################################
+% #########################################################################################
 % #########################################################################################

### 2025-04-26 Neural-Manifolds/neural-manifolds_v0.tex
aiaiaiai

@@
 
-These representations can be expressed as manifolds.
-
-As it tranverses the manifold we observe a change of phase which can be descirbed in information geometry and the former statistical mechanics as related to likelihood.
+These representations can be expressed as manifolds (low-dimensional representations of behavioral signals in neural population activity).
+
+As it traverses the manifold we observe a change of phase which can be described in information geometry and the former statistical mechanics as related to likelihood.
 (attention to the Hodge operator).
-If we consider that there are many paths to start at a simplicial representation and to achive a simplicial go and the path is the computation.
+If we consider that there are many paths to start at a simplicial representation and to achieve a simplicial goal, and the path is the computation.
 We can say that all computations that are within the path of least ACTION constructively interferes and all other paths destructively interferes.
@@
 Need to extend the Approximate Bayesian Computation (ABC)
+
+This property is observed in brain as the complex and heterogeneous activity of the underlying circuit mechanism only hints that the computation is happening at a lower dimensional abstract representation that is part of the much larger encoded information, a subset.
+
+Further research has demonstrated properties and the geometry of this structure.
+
+There is also evidence of the Approximate Bayesian Computation (ABC) extended to Information geometry where the computation is the active mechanism of the brain trying to fit the likelihood of the encoded model vs the generated model.
+Which can be described as the translation in the manifolds.
+The high dimensional encoded space allows for the emergence of these structures which are relative and have a relative entropy between both models.
+
+We can see that behavior between cortex and hypocampus.
+
+dorsomedial prefrontal cortex (dmPFC) and hypocampus for the Temporal Estimation task.
+
+Other areas work similarly.
+
+In other words, individual neurons although its complexity are biased to form (groups or populations or clusters) whose (activation or firing pattern) can be represented as a dynamical system trying to perform a particular operation (there are a few), and these (groups or populations or clusters) are biased to form larger (groups or populations or clusters) whose (activation or firing pattern) goal is trying to find the path of least action through percolation properties of this complex network and these mechanics can be best described by Lagrangian mechanics.
+
+There are so many cool parts of the percolation in this case.
+It is bound by the geometry, it is described by the least action, the distribution can be described by an extended version of the ABC, it has nice well explored properties which can be borrowed from the Ising model, the high dimensionality has nice properties like emergency of fractals among many things.
 
